---
title: "ConsumptionEDA"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Read in Data

```{r}
library(ggplot2)
library(reshape2)
library(car)
require(dplyr)
library(Hmisc)
#setwd('C:/Users/eyang/Desktop')
consumption_data = read.csv('2012_public_use_data_aug2016.csv')

data_small =subset(consumption_data, NWKER <= 200 & SQFT <= 500000 & FREESTN == 1 & ONEACT == 1)

data_small$PBA_NAME <- as.factor(ifelse(data_small$PBA == 1, 'Vacant', 
                       ifelse(data_small$PBA == 2, 'Office',
                       ifelse(data_small$PBA == 4, 'Lab',
                       ifelse(data_small$PBA == 5, 'Warehouse No Fridge',
                       ifelse(data_small$PBA == 6, 'Food Sales',
                       ifelse(data_small$PBA == 7, 'Public Order',
                       ifelse(data_small$PBA == 8, 'Outpatient',
                       ifelse(data_small$PBA == 11, 'Warehouse',
                       ifelse(data_small$PBA == 12, 'Religious',
                       ifelse(data_small$PBA == 13, 'Public Assembly',
                       ifelse(data_small$PBA == 14, 'Education',
                       ifelse(data_small$PBA == 15, 'Food Service',
                       ifelse(data_small$PBA == 16, 'Inpatient',
                       ifelse(data_small$PBA == 17, 'Nursing',
                       ifelse(data_small$PBA == 18, 'Lodging',
                       ifelse(data_small$PBA == 23, 'Strip Mall',
                       ifelse(data_small$PBA == 24, 'Enclosed Mall',
                       ifelse(data_small$PBA == 25, 'Retail',
                       ifelse(data_small$PBA == 26, 'Service','Other'))))))))))))))))))))

data_small$GEO  <-  as.factor(ifelse(data_small$CENDIV == 1, 'New England',
                       ifelse(data_small$CENDIV == 2, 'Middle Atlantic',
                       ifelse(data_small$CENDIV == 3, 'East North Central',
                       ifelse(data_small$CENDIV == 4, 'West North Central',
                       ifelse(data_small$CENDIV == 5, 'South Atlantic',
                       ifelse(data_small$CENDIV == 6, 'East South Central',  
                       ifelse(data_small$CENDIV == 7, 'West South Central',
                       ifelse(data_small$CENDIV == 8, 'Mountain',
                       ifelse(data_small$CENDIV == 9, 'Pacific',''))))))))))

data_small$HRS24 = ifelse(data_small$OPEN24 == 1, 1,0)
data_small$OPNWE = ifelse(data_small$OPNWE == 1, 1, 0)
data_small$ELHT1 = ifelse(data_small$ELHT1 == 1, 1, 0)
data_small$EMCS = ifelse(data_small$EMCS == 1, 1, 0)
data_small$ELWATR = ifelse(data_small$ELWATR == 1, 1, 0)
data_small$ELCOOK = ifelse(data_small$ELCOOK == 1, 1, 0)
data_small$ELMANU = ifelse(data_small$ELMANU == 1, 1, 0)
data_small$KITCHN= ifelse(data_small$KITCHN == 1, 1, 0)
data_small$RFGEQP= ifelse(data_small$RFGEQP == 1, 1, 0)
data_small$PCTERM= ifelse(data_small$PCTERM== 1, 1, 0)
data_small$SERVER= ifelse(data_small$SERVER== 1, 1, 0)
data_small$TVVIDEO= ifelse(data_small$TVVIDEO== 1, 1, 0)
data_small$COPIER= ifelse(data_small$COPIER== 1, 1, 0)
data_small$OCSN = ifelse(data_small$OCSN== 1, 1, 0)

data_small$NELVTR[is.na(data_small$NELVTR)] = 0
data_small$NESLTR[is.na(data_small$NESLTR)] = 0

length(data_small$PUBID)

head(data_small$PBA_NAME)

table(data_small$PBA_NAME)

```
#(NELVTR, NESLTR, WKHRS, OPEN24, ELHT1,OPNWE, ELCOOL, EMCS, ELWATR, ELCOOK, ELMANU, RFGEQP, PCTERM, PCTERMN, SERVER, SERVERN, TVVIDEO, TVVIDEON, COPIER, COPIERM, LTOHRP,OCSN, WINTYP)

#Specific to Office
KITCHN

#Specific to Med
XRAYN, CTSCAN, MRI, OUTSURG, LABEQP


#check fields
```{r}
head(data_small)
summary(data_small$PBA)
```

#EDA
```{r}
hist(log(data_small$ELCNS), main="Log Commercial Electricity Consumption 2012")
```
There are some big outliers in the dataset in terms of annual electricity usage

```{r}
ggplot(data_small, aes(x=REGION, y=log(ELCNS), group=REGION)) + geom_boxplot()+
ylab("")+xlab("Region")+ggtitle("Boxplot of Annual Electricity Consumption by Region")
```
Not a huge difference in the distribution.  Northeast highest median, west is the lowest median

```{r}
ggplot(data_small, aes(x=CENDIV, y=log(ELCNS), group=CENDIV)) + geom_boxplot()+
ylab("")+xlab("Census Division")+ggtitle("Boxplot of Annual Electricity Consumption by Census Division")
```
A little more variation when we cut by census division

```{r}
ggplot(data_small, aes(x=log(SQFT), y=log(ELCNS)))+
  geom_point()+geom_smooth(method="loess")+ggtitle("SQFT vs. Annual Electricity Usage")
```
A little more variation when we cut by census division

```{r}
table(data_small$SQFTC)
```
The dataset has nothing under 1000 sqft

```{r}
data.frame(table(data_small$PBA_NAME))
```
Sample by Business Type

```{r}
ggplot(data_small, aes(x=PBA_NAME, y=log(ELCNS), group=PBA_NAME)) + geom_boxplot()+
ylab("")+xlab("Primary Business Activity")+ggtitle("Boxplot of Annual Electricity Consumption by Primary Business Activity")+ theme(axis.text.x = element_text(angle = 60, hjust = 1))
```


```{r}
ggplot(data_small, aes(x=log(NWKER), y=log(ELCNS)))+
  geom_point()+geom_smooth(method="loess")+ggtitle("Number of Workers vs. Annual Electricity Usage")
```



```{r}
data_yr = data_small[data_small$YRCON != 995,]
ggplot(data_yr, aes(x=YRCON, y=log(ELCNS)))+
  geom_point()+geom_smooth(method="loess")+ggtitle("Year Constructed vs. Annual Electricity Usage")
```


```{r}
options(warn=-1)
ggp <- ggplot(data_small, aes(x=SQFT, y=ELCNS,
                                     color=PBA_NAME))

ggp + geom_point(aes(color=PBA_NAME))+
  geom_smooth(method="loess", se=F)+
  ylab("Annual Electricity Usage")+
  xlab("Sqft")+
  ggtitle("Annual Electricity Usage by Business type squarefootage")+
  theme(plot.title=element_text(hjust=.5))
```


```{r}
#Combined Model
consump_fit = lm(ELCNS ~ SQFT + YRCON + NWKER + GLSSPC + WKHRS + relevel(PBA_NAME, ref = 'Vacant') + relevel(GEO, ref = 'Pacific'), data = data_small)
summary(consump_fit)
```
#(NELVTR, NESLTR, WKHRS, OPEN24, ELHT1,OPNWE, ELCOOL, EMCS, ELWATR, ELCOOK, ELMANU, RFGEQP, PCTERM, PCTERMN, SERVER, SERVERN, TVVIDEO, TVVIDEON, COPIER, COPIERM, LTOHRP,OCSN, WINTYP)
```{r}
#Food Sales Model
data_food_sales =subset(data_small, PBA_NAME == 'Food Sales')
length(data_food_sales$PUBID)

food_sales_fit = lm(ELCNS ~ SQFT + YRCON + NWKER + GLSSPC + WKHRS + OPEN24 + NELVTR + NESLTR + OPNWE + ELHT1 + ELCOOL + ELWATR + ELCOOK + ELMANU + RFGEQP, data = data_food_sales)

summary(food_sales_fit)
```
```{r}
#Warehouse Model
data_warehouse =subset(data_small, PBA_NAME == 'Warehouse No Fridge')
length(data_warehouse$PUBID)

warehouse_fit = lm(ELCNS ~ SQFT + YRCON + NWKER + GLSSPC + WKHRS + OPEN24 + NELVTR + NESLTR + OPNWE + ELHT1 + ELCOOL + ELWATR + ELCOOK + ELMANU + RFGEQP, data = data_warehouse)

summary(warehouse_fit)
```



```{r}
#Office Model
data_office =subset(data_small, PBA_NAME == 'Strip Mall')
length(data_office$PUBID)

office_fit = lm(ELCNS ~ SQFT + YRCON + NWKER + GLSSPC + WKHRS + OPEN24 + NELVTR + NESLTR + OPNWE + ELHT1 + ELCOOL + ELWATR + ELCOOK + ELMANU + RFGEQP, data = data_office)

summary(office_fit)
```